---
title: "Analysis of Selected Libraries"
author: "David Jackson"
date: "9/27/2021"
output: 
  html_document: 
    fig_width: 9
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(scales)
library(CGPfunctions)
library(lsr)
library(readODS)
```

### Hypothess:

"A supposition or proposed explanation made on the basis of limited evidence as a starting point for further investigation."

### What is the Null Hypothesis?

" The null hypothesis states that there is no relationship between two population parameters, i.e., an independent variable and a dependent variable. If the hypothesis shows a relationship between the two parameters, the outcome could be due to an experimental or sampling error. However, if the null hypothesis returns false, there is a relationship in the measured phenomenon." (https://corporatefinanceinstitute.com/)

### What is Our Null Hypothesis?

That there is no relationship between race (of the main charactors) and
the purchasing habits of sixteen selected library branches.

### The p-value explained

The p-value is a number, calculated from a statistical test, that describes how likely you are to have found a particular set of observations if the null hypothesis were true.

P-values are used in hypothesis testing to help decide whether to reject the null hypothesis. The **smaller the p-value **, the more likely you are to **reject** the null hypothesis.

```{r}
branch_pvalues <- tibble::tribble(
               ~Branch,          ~`P-value`,
               "bkcta",             2.2e-16,
               "cdctc",           5.294e-09,
               "cdctb",           6.282e-09,
               "bkctd",           1.296e-08,
               "bkctc",           3.052e-08,
               "cdctd",           1.586e-06,
               "cdctf",           3.977e-05,
               "cdcta",           0.0001024,
               "bkcte",           0.0001135,
             "dig_ctc",           0.0002242,
             "dig_ctd",           0.0004499,
               "cdcte",            0.001836,
             "dig_cta",             0.00276,
             "dig_cte",            0.008088,
             "dig_ctf",             0.01091,
  "Race is not factor",                0.04,
               "bkctf",              0.0422,
                "bk_b",             0.05248,
             "dig_ctb",              0.5297
  ) 

branch_pvalues %>% 
    flextable::flextable()

```

## Analysis of Audio books by Race of Main Character



```{r}
rm(list=ls())
df <- readxl::read_xlsx("./LibraOfficeAudioBookDataFinal.xlsx")
# df <- read_ods("./AudioBookDataODS.ods")
df <- janitor::clean_names(df) # Use Janitor to clean col names
df$dig_ctf<-substr(df$dig_ctf,1,1)
df$dig_ctb<-substr(df$dig_ctb,1,1)
df$dig_cta<-substr(df$dig_cta,1,1)
df$dig_ctc<-substr(df$dig_ctc,1,1)
df$dig_ctd<-substr(df$dig_ctd,1,1)
df$dig_cte<-substr(df$dig_cte,1,1)
```

## Branches Where Null Hypothesis wasn't rejected (P > 0.40)

### Branch Library: bkctf

```{r}

# par(mfrow = c(1,2))
bkctf <- table(df$race,df$bkctf)
plot(bkctf)
barplot(bkctf,legend=TRUE)
chisq.test(bkctf,correct = TRUE)
```
```{r}
bkctf <- as.data.frame(bkctf)
ggplot(bkctf) + geom_col(aes(x=Var2,y=Freq,fill=Var1))

```




### Branch Library: bk_b

```{r}
# par(mfrow = c(1,2))
bk_b <- table(df$race,df$bk_b)
plot(bk_b)
barplot(bk_b,legend=TRUE)
chisq.test(bk_b,correct = TRUE)
```

```{r}
bk_b <- as.data.frame(bk_b)
ggplot(bk_b) + geom_col(aes(x=Var2,y=Freq,fill=Var1))

```

### Branch Library: dig_ctb

```{r}
# par(mfrow = c(1,2))
dig_ctb <- table(df$race,df$dig_ctb)
plot(dig_ctb)
barplot(dig_ctb,legend=TRUE)
chisq.test(dig_ctb,correct = TRUE)
```
```{r}
dig_ctb <- as.data.frame(dig_ctb)
ggplot(dig_ctb) + geom_col(aes(x=Var2,y=Freq,fill=Var1))

```


## Branches Where Null Hypothesis was Rejected (P < 0.04)

### Branch Library: bkcta

```{r}
# par(mfrow = c(1,2))
bkcta <- table(df$race,df$bkcta)
plot(bkcta)
barplot(bkcta,legend=TRUE)
chisq.test(bkcta,correct = TRUE)
table(df$bkcta)

```

```{r}
bkcta <- as.data.frame(bkcta)
ggplot(bkcta) + geom_col(aes(x=Var2,y=Freq,fill=Var1))

```


### Branch Library: cdcta

```{r}
par(mfrow = c(1,2))
cdcta <- table(df$race,df$cdcta)
plot(cdcta)
barplot(cdcta,legend=TRUE)

chisq.test(cdcta,correct = TRUE)
```

### Branch Library: dig_cta

```{r}
par(mfrow = c(1,2))
dig_cta <- table(df$race,df$dig_cta)
plot(dig_cta)
barplot(dig_cta,legend=TRUE)
chisq.test(dig_cta,correct = TRUE)

```





### Branch Library: cdctb

```{r}
par(mfrow = c(1,2))
cdctb <- table(df$race,df$cdctb)
plot(cdctb)
barplot(cdctb,legend=TRUE)
chisq.test(cdctb,correct = TRUE)
```



### Branch Library: bkctc

```{r}
par(mfrow = c(1,2))
bkctc <- table(df$race,df$bkctc)
plot(bkctc)
barplot(bkctc,legend=TRUE)
chisq.test(bkctc,correct = TRUE)
```

### Branch Library: cdctc

```{r}
par(mfrow = c(1,2))
cdctc <- table(df$race,df$cdctc)
plot(cdctc)
barplot(cdctc,legend=TRUE)
chisq.test(cdctc,correct = TRUE)

```

### Branch Library: dig_ctc

```{r}
par(mfrow = c(1,2))
dig_ctc <- table(df$race,df$dig_ctc)
plot(dig_ctc)
barplot(dig_ctc,legend=TRUE)
chisq.test(dig_ctc,correct = TRUE)

```

### Branch Library: bkctd

```{r}
par(mfrow = c(1,2))
bkctd <- table(df$race,df$bkctd)
plot(bkctd)
barplot(bkctd,legend=TRUE)
chisq.test(bkctd,correct = TRUE)

```

### Branch Library: cdctd

```{r}
par(mfrow = c(1,2))
cdctd <- table(df$race,df$cdctd)
plot(cdctd)
barplot(cdctd,legend=TRUE)
chisq.test(cdctd,correct = TRUE)
```

### Branch Library:dig_ctd

```{r}
par(mfrow = c(1,2))
dig_ctd <- table(df$race,df$dig_ctd)
plot(dig_ctd)
barplot(dig_ctd,legend=TRUE)
chisq.test(dig_ctd,correct = TRUE)
```

### Branch Library: cdcte

```{r}
par(mfrow = c(1,2))
cdcte <- table(df$race,df$cdcte)
plot(cdcte)
barplot(cdcte,legend=TRUE)
chisq.test(cdcte,correct = TRUE)
```

### Branch Library: dig_cte

```{r}
par(mfrow = c(1,2))
dig_cte <- table(df$race,df$dig_cte)
plot(dig_cte)
barplot(dig_cte,legend=TRUE)
chisq.test(dig_cte,correct = TRUE)
```



### Branch Library: cdctf

```{r}
par(mfrow = c(1,2))
cdctf <- table(df$race,df$cdctf)
plot(cdctf)
barplot(cdctf,legend=TRUE)
chisq.test(cdctf,correct = TRUE)
```


### Branch Library: dig_ctf

```{r}
par(mfrow = c(1,2))
dig_ctf <- table(df$race,df$dig_ctf)
plot(dig_ctf)
barplot(dig_ctf,legend=TRUE)
chisq.test(dig_ctf,correct = TRUE)

```



