---
title: "Books"
author: "David Jackson"
date: "5/5/2021"
output: 
  pdf_document: 
    fig_width: 8
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)
library(dlookr)
```

## Can Children of Different Races “See” Themselves in Audiobooks? A Comparison of U.S. Library Systems’ Offerings

* bulleted text

Numbers $x2%$


```{r}
rm(list=ls())
df <- readxl::read_xlsx("./AudioBookDataFinal.xlsx")
df <- janitor::clean_names(df) # Use Janitor to clean col names

```
```{r}
awards <- df %>% select()
awards <- df %>% select(yr:author,newberry:aila)

awards_count <- awards %>% group_by(author) %>% summarise(
        across(newberry:aila,sum))

awards_long <- awards_count %>% pivot_longer(cols = newberry:aila)
```

```{r}
awards_count %>% filter(csk >=2) %>%
  ggplot() + geom_col(aes(x=author,y=csk)) + coord_flip()
```

```{r}
awards_long %>% filter(value >=3) %>%
  ggplot() + geom_col(aes(x=name,y=value))  +
  facet_wrap(~author,ncol = 3,scales ="free")
```

### ABSTRACT

```{r}

```

### Introduction

```{r}

```

### Literature review

```{r}

```

### Method

```{r}

```

#### Data source

#### Search procedure

#### Data analysis

```{r}
YR <- table(df$yr)
YR <- as.data.frame(YR)
ggplot(YR) + geom_col(aes(x=Var1,y=Freq)) + coord_flip()
yr_tibble <- tibble(YR)
```

```{r}
TAB <-table(df$author)
TAB <- as.data.frame(TAB)
top_five <- TAB %>% top_n(10)
ggplot(top_five) + geom_col(aes(x=Var1,y=Freq)) + coord_flip()
```
```{r}
count_race <-table(df$race)
prop_race <- prop.table(count_race)
prop_race_df <- as.data.frame(prop_race)
ggplot(prop_race_df) + geom_col(aes(x=Var1,y=Freq)) + coord_flip() +
  scale_y_continuous(labels = percent)
```

#### Determining race and/or ethnicity of primary characters

```{r}

```

#### Selecting comparison cities and library systems

```{r}

```

#### Search procedure

```{r}

```

#### Data analysis

```{r}

```

### Results

#### Market availability of audiobooks

```{r}

```

#### Library availability of audiobooks featuring white, Black, Latino/a, and
Asian/Pacific characters

```{r}

```

#### Library availability of audiobooks featuring white characters versus
characters of color


```{r}

```

### Discussion

```{r}

```

####  Market availability of audiobooks

```{r}

```

#### Library availability of audiobooks

```{r}

```

#### Comparing books featuring white characters/characters of color

```{r}

```

### Limitations and recommendations for future research

```{r}

```

#### Conclusion

```{r}

```


#### Notes


#### Acknowledgement

#### Disclosure statement

#### ORCID

#### References

#### Literature cited

#### Appendix. Award-Winning Children’s Novels (1996-2018).








